On the combination of Set Functions and Failures

### 2013-10-30 docs/src/usage.tex
Change manual to mention the option as 'parallel'

\item[\fbox{\code{par}}]\pindex{par}
Similarly to \code{bfs} but use a parallel search strategy
to compute and print the values of the initial expression.
The system chooses an appropriate number
of threads according the current number of available processors.

\item[\fbox{\code{par $n$}}]\pindex{par}
Similarly to \code{par} but use $n$ parallel threads.

>>>>

\item[\fbox{\code{parallel}}]\pindex{parallel}
Similarly to \code{bfs} but use a parallel search strategy
to compute and print the values of the initial expression.
The system chooses an appropriate number
of threads according the current number of available processors.

\item[\fbox{\code{parallel $n$}}]\pindex{parallel}
Similarly to \code{parallel} but use $n$ parallel threads.
